\documentclass[singlecolumn,singlespace,11pt]{article}
\usepackage[dvipsnames]{xcolor}
\usepackage[T1]{fontenc}
\usepackage{multicol}
\usepackage{marvosym} % For cool symbols.
\usepackage{mathptmx}
\usepackage{hyperref}
\usepackage{paracol}
\usepackage{titling}
\setlength{\droptitle}{-5em}
\usepackage{lipsum}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\setlength{\headsep}{0pt}
\setlength{\topskip}{0pt}
\setlength{\topmargin}{0pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\linespread{0.5}
\renewcommand{\baselinestretch}{1}
\newcommand{\ignore}[1]{}
%\usepackage[compact]{titlesec}
%\titlespacing{\section}{0pt}{*0}{*0}
%\titlespacing{\subsection}{0pt}{*0}{*0}
%\titlespacing{\subsubsection}{0pt}{*0}{*0}
\usepackage{graphicx}
\usepackage{url}
\usepackage{verbatim}
\usepackage{color}
\usepackage[top=2cm, bottom=2cm]{geometry}


\begin{document}
\title{ { \bfseries Curriculum Vitae} }
%\author{Shoaib Akram\\
%        \texttt{Shoaib.Akram@UGent.be}\\
%	\url{users.elis.ugent.be/~sakram}
%       }
\author{Shoaib Akram\\
	Australian National University \\
        \texttt{Shoaib.Akram@anu.edu.au} \\
        \texttt{https://shbakram.github.io}
       }
\date{}
\maketitle

\section*{Education}
\noindent Ph.D. Computer Science Engineering, Ghent University, 2019. \\
Advisor: Lieven Eeckhout (IEEE \& ACM Fellow)  \\
Thesis Topic: Exploiting Managed Language Semantics to Optimize for Hardware Heterogeneity
\\
\\
\noindent M.S. Electrical and Computer Engineering, University of Illinois at Urbana-Champaign, 2009. \\
Advisor: Deming Chen (IEEE Fellow) \\
Thesis Topic: Workload Adaptive Shared Memory Multicore Processors with Reconfigurable Interconnects
\\
\\
\noindent B.Sc. Electrical Engineering, University of Engineering \& Technology, Lahore, Pakistan, 2006.\\
Advisor: Shahid H. Bokhari (IEEE \& ACM Fellow) \\
Thesis Topic: Implementation of Suffix Trees on FPGAs 

\section*{Research Interests} 
Computer architecture; Memory and storage systems; Performance analysis
\ignore{
\\
\\
\noindent \textbf{Summary of Current Research:} My current research explores storage engines for data-intensive applications.
I am especially interested in how fast storage devices (e.g., NVMe SSDs) reshape the internal design of databases and search engines.
\\
\\
\noindent \textbf{Contributions of Previous Research:}
My Ph.D. research has also investigated energy-efficient execution of managed
workloads on modern hardware. My contributions include scheduling for
heterogeneous multicores and performance prediction of frequency scaling for multithreaded workloads.
Before starting my Ph.D., I explored the sources of inefficiency in the
software stack of a distributed stream processing system.  My research and
development efforts contributed a software stack for energy efficient data
stream processing. My previous research has also proposed a novel methodology
for quantifying the efficiency of datacentric infrastructures.
}

%\section*{Research Appointments}
\section*{Employment}
\begin{minipage}{\linewidth}
\noindent \textbf{January 2020 - Current}\\
%Lecturer (Assistant Professor) at The Australian National University \\
Lecturer at The Australian National University \\
\end{minipage}
\\
\\
\\
\begin{minipage}{\linewidth}
\noindent \textbf{July 2019 - December 2019}\\
Post-doctoral Researcher at PerfLab - Ghent University \\
\end{minipage}
\\
\\
\\
\begin{minipage}{\linewidth}
\noindent \textbf{July 2012 - June 2019}\\
Ph.D. student at PerfLab - Ghent University \\
Research Focus: Computer architecture, runtime systems, memory management
\end{minipage}
\\
\\
\\
\begin{minipage}{\linewidth}
\noindent \textbf{March 2010 - June 2012}\\
Junior Researcher at FORTH-ICS, Greece (with Angelos Bilas) \\
Research Focus: Storage systems
\end{minipage}
\\
\\
\\
\begin{minipage}{\linewidth}
\noindent \textbf{March 2006 - May 2007}\\
Research Associate, Al-Khwarizmi Institute of Computer Science (KICS), Lahore\\
%FPGA Research and Development: Error correction in an in-house software defined radio (1000+ lines of VHDL code) 
\end{minipage}

\section*{Memberships}

\begin{itemize}
\item Professional Member, Association for Computing Machinery (ACM)
\end{itemize}

\section*{Refereed Publications}
\subsection*{Journals}
\begin{enumerate}
\item
A. Hasnat, \textbf{S. Akram}, ``SPIRIT: Scalable and Persistent In-Memory Indices for Real-Time Search,'' ACM Transactions on Architecture and Code Optimization (TACO), 2025.
\item 
I. Kolokasis, G. Evdorou, \textbf{S. Akram}, A. Papagiannis, F. Zakkak, C. Kozanitis, P. Pratikakis, A. Bilas, ``TeraHeap: Exploiting Flash Storage for Mitigating DRAM Pressure in Managed Big Data Frameworks,'' ACM Transactions on Programming Languages and Systems (TOPLAS), 2025. 

\item
W. Liu, W. Heirman, S. Eyerman, \textbf{S. Akram}, and L. Eeckhout, ``Scale-Model Simulation,'' IEEE Computer Architecture Letters (CAL), 2021.
\item
\textbf{S. Akram}, ``Performance Evaluation of Intel Optane Memory for Managed Workloads,'' ACM Transactions on Architecture and Code Optimization (TACO), 2021.
\item
W. Liu, \textbf{S. Akram}, and L. Eeckhout, ``Reliability-Aware Garbage Collection for Hybrid DRAM-HBM Memories,'' ACM Transactions on Architecture and Code Optimization (TACO), 2021.
\item
S. Pestel, S. Steen, \textbf{S. Akram}, and L. Eeckhout, ``RPPM: Rapid Performance Prediction of Multithreaded Applications on Multicore Hardware,'' IEEE Computer Architecture Letters (CAL), 2018.
\item
\textbf{S. Akram}, J. Sartor, and L. Eeckhout, ``DEP+BURST: Online DVFS Performance Prediction for Energy-Efficient Managed Language Execution," IEEE Transactions on Computers (TC), 2017.
\item
\textbf{S. Akram}, J. Sartor, K. Van Craeynest, W. Heirman, and L. Eeckhout, ``Boosting the Priority of Garbage: Scheduling Collection on Heterogeneous Multicore Processors," ACM Transactions on Architecture and Code Optimization (TACO), 2016.
\item
\textbf{S. Akram}, A. Papakonstantinou, R. Kumar, D. Chen, ``S. Akram, A. Papakonstantinou, R. Kumar, D. Chen, "A Workload-adaptive and Reconfigurable Bus Architecture for Multicore Processors," 
International Journal of Reconfigurable Computing (IJRC), 2010.
\end{enumerate}
\subsection*{Conferences}
\begin{enumerate}
%\setcounter{enumi}{4}

\item
Aditya Chilukuri and \textbf{Shoaib Akram}, ``Analyzing and Improving the Scalability of In-Memory Indices for Managed Search Engines,'' ACM SIGPLAN International Symposium on Memory Management (ISMM), 2023. {\color{blue} Acceptance Rate: 13/25}
\\
{\color{BrickRed} \textbf{$\longrightarrow$ \emph{Best Paper Candidate}}}

\item 
I. Kolokasis, G. Evdorou, \textbf{S. Akram}, A. Papagiannis, F. Zakkak, C. Kozanitis, P. Pratikakis, A. Bilas, ``TeraHeap: Reducing Memory Pressure in Managed Big Data Frameworks,'' Architectural Support for Programming Languages and Operating Systems (ASPLOS), 2023. {\color{blue} Acceptance Rate: 128/598}

\item
W. Liu, W. Heirman, S. Eyerman, \textbf{S. Akram}, and L. Eeckhout,
``Scale-Model Architectural Simulation,'' IEEE International Symposium on
Performance Analysis of Systems and Software (ISPASS), 2022. {\color{blue} Acceptance Rate: 24/83}

\item
\textbf{S. Akram}, ``Exploiting Intel Optane Persistent Memory for Full Text Search," ACM SIGPLAN International Symposium on Memory Management (ISMM), 2021. {\color{blue} Acceptance Rate: 8/14}

\item
S. Pestel, S. Steen, \textbf{S. Akram}, and L. Eeckhout, ``RPPM: Rapid Performance Prediction of Multithreaded Workloads on Multicore Processors," IEEE International Symposium on Performance Analysis of Systems and Software (ISPASS), 2019. {\color{blue} Acceptance Rate: 26/88}

\item
\textbf{S. Akram}, J. Sartor, K. McKinley and L. Eeckhout, ``Emulating and Evaluating Hybrid Memory for Managed Languages on NUMA Hardware," IEEE International Symposium on Performance Analysis of Systems and Software (ISPASS), 2019. {\color{blue} Acceptance Rate: 26/88}

\item 
\textbf{S. Akram}, J. Sartor, K. McKinley and L. Eeckhout, ``Crystal Gazer: A Profile-Driven Garbage 
Collector to Manage Hybrid Memories," ACM International Conference on Measurement and Modeling of Computer Systems
(SIGMETRICS), 2019. {\color{blue} Acceptance Rate: 50/317}

\item
\textbf{S. Akram}, J. Sartor, K. McKinley and L. Eeckhout, ``Write-Rationing Garbage Collection for Hybrid Memories," ACM SIGPLAN Conference on Programming Language Design and Implementation (PLDI), 2018. {\color{blue} Acceptance Rate: 55/245}
\\
{\color{BrickRed} \textbf{$\longrightarrow$ \emph{NVMW Memorable Paper Award}}}

\item
\textbf{S. Akram}, J. Sartor, and L. Eeckhout, ``DVFS Performance Prediction for Managed Multi-Threaded Applications," IEEE International Symposium on Performance Analysis 
of Systems and Software (ISPASS), 2016. {\color{blue} Acceptance Rate: 27/77} 
\\
{\color{BrickRed} \textbf{$\longrightarrow$ \emph{Best Paper Candidate}}}

\item
K. Van Craeynest, \textbf{S. Akram}, W. Heirman, A. Jaleel, and L. Eeckhout, ``Fairness-aware Scheduling on Single-ISA Heterogeneous Multicores," 
International Conference on Parallel Architectures and Compilation Techniques (PACT), 2013. {\color{blue} Acceptance Rate: 36/208}

\item
\textbf{S. Akram}, M. Marazakis, and A. Bilas, ``Understanding Scalability and Performance Requirements of I/O-intensive Applications
on Future Multicore Servers," IEEE International Symposium on Modeling, Analysis and Simulation of Computer and 
Telecommunication Systems (MASCOTS), 2012. {\color{blue} Acceptance Rate: 49/134}

\item 
\textbf{S. Akram}, M. Marazakis, and A. Bilas, ``Understanding and Improving the Cost of Scaling Distributed Event Processing," 
ACM International Conference on Distributed Event-Based Systems (DEBS), 2012. {\color{blue} Acceptance Rate: 17/103}

\item
\textbf{S. Akram}, R. Kumar, D. Chen, ``Workload Adaptive Shared Memory Multicore Processors with Reconfigurable Interconnects,"
IEEE Symposium on Application Specific Processors (SASP), 2009. 


\end{enumerate}

\subsection*{Poster/Workshop}
\begin{enumerate}

\item
Iacovos G. Kolokasis, \textbf{Shoaib Akram}, Foivos Zakkak, Polyvios Pratikakis, and Angelos Bilas, ``DynaHeap: Dynamic Division of DRAM between Heterogeneous Managed Heaps,"
Symposium on Operating System Principles (SOSP), 2023. 

\item
\textbf{S. Akram} and A. Bilas, ``Energy Implications of Contention in Multicore Processors for the Data-Centre,"
EuroSys, 2012.

\item
\textbf{S. Akram} and A. Bilas, ``A Sleep-based Communication Mechanism to Save Processor Utilization in Distributed Streaming Systems,"
Computer Architecture and Operating System Co-design (CAOS), held alongside HiPEAC, 2011.


\item
\textbf{S. Akram} and A. Bilas, ``A Sleep-based Communication Mechanism to Save Processor Utilization in Distributed Streaming Systems,"
Computer Architecture and Operating System Co-design (CAOS), held alongside HiPEAC, 2011.

\item
\textbf{S. Akram}, M. Marazakis, and A. Bilas, ``NUMA Implications for Storage I/O Throughput in Modern Servers," 
Computer Architecture and Operating System Co-design (CAOS), held alongside HiPEAC, 2012. 

\item
\textbf{S. Akram}, M. Marazakis, and A. Bilas, ``Energy Inefficiency of Operating System Layers for Data-centric Infrastructures," Systems for Future Multi-core Architectures (SFMA), held alongside EuroSys, 2012.
\item
\textbf{S. Akram}, K. McKinley, J. Sartor, and L. Eeckhout, ``Managing Hybrid Memories by Predicting Object Write Intensity," Programming Across the System Stack (PASS), held alongside <programming>, 2018.

\item
\textbf{S. Akram}, ``To Expose, or Not to Expose, Hardware Heterogeneity to Runtimes!" Modern Language Runtimes, Ecosystems, and VMs (MoreVMs), held alongside <programming>, 2019.
\end{enumerate}

\subsection*{Invited Publications}
\begin{enumerate}
\item
\textbf{S. Akram}, J. Sartor, K. McKinley and L. Eeckhout, ``Kingsguard: Write-Rationing Garbage Collection for Hybrid Memories," Annual Non-Volatile Memories Workshop (NVMW), 2019. 

\item
\textbf{S. Akram}, S. Cromar, G. Lucas, A. Papakonstantinou, and D. Chen, ``VEBoC: Variation and Error-Aware Design for Billions of Devices on a Chip," 
IEEE/ACM Asia and South Pacific Design Automation Conference (ASPDAC), 2008.
\end{enumerate}


\section*{Invited Talks}
\begin{enumerate}
\item ``Exploiting Managed Language Semantics to Mitigate Wear-Out in Persistent Memory," Flash Memory Summit, 2019, Santa Clara.
\item ``Exploiting Managed Language Semantics to Optimize for Heterogeneous Hardware," Australian National University, 2019, Canberra.
\item ``Kingsguard: Write-Rationing Garbage Collection for Hybrid Memories," Annual Non-Volatile Memories Workshop (NVMW), 2019, San Diego.
\item ``Profile-Driven Write-Rationing Garbage Collection for Hybrid Memories," The 5th Virtual Machine Meetup (VMM), 2018, Linz.
\item ``Write-Rationing Garbage Collection for Hybrid Memories," Swiss Federal Institute of Technology, 2018, Lausanne.
\item ``Write-Rationing Garbage Collection for Hybrid Memories," The 4th Virtual Machine Meetup, 2017, Prague.
\item ``Managed Language Runtimes on Heterogeneous Hardware: Optimizations for Performance, Efficiency and Lifetime Improvement," Workshop on Programming Across the System Stack (PASS), 2017, Brussels.
\item ``DVFS Performance Prediction for Managed Multithreaded Applications," VSSAD seminar, Sep. 15, 2017, Intel, Portland.
\item ``Energy-Efficient Managed Language Execution on Modern Hardware," The 3rd Virtual Machine Meetup (VMM), 2016, Lugano.
\end{enumerate}


\section*{Achievements and Honors}
\begin{itemize}
\item HiPEAC Paper Award for ASPLOS 2023
\item Nominated for Best Paper Award at ISMM 2023
\item NVMW Memorable Paper Award 2019
\item HiPEAC Paper Award for PLDI 2018 
\item Nominated for Best Paper Award at ISPASS 2016 
\item Marie Curie Initial Training Networks Fellowship (2010-2012)
\item Fulbright Scholarship (2007-2009)
\item Graduated from the University of Engineering and Technology with Honors (2006)
\item First position in college, Crescent Model Higher Secondary School, Lahore, Pakistan (2001)
\end{itemize}

\section*{Service (ANU)}

\begin{itemize}
\item Ph.D. Scholarship Ranking Committee (Research School of Computer Science, August 2020)
\item HDR Convener (ANU School of Computing, Foundations cluster, 2021)
\end{itemize}

\section*{Ph.D. Supervisory Panel (ANU)}

\begin{itemize}
\item Wenyu Zhao (Advisor: Steve Blackburn)
\end{itemize}

\section*{Ph.D. Advisees}
University of Crete, Department of Computer Science, 2020 \\
\indent Iacovos G. Kolokasis (Co-Advisor and Ph.D. committee) \\
\indent Advisor: Angelos Bilas \\ 
\indent Thesis Topic: Efficient Caching for Big Data Analytics \\ 
\indent Awards: Meta (Facebook) Research PhD Fellowship (2022)
\\
\\
Australian National University, School of Computing, 2024\\
\indent Jackson Kilrain-Mottram \\
\indent Thesis Topic: Storage Engines for Managed Data-Intensive Frameworks

\section*{Honours Students (ANU)}

\begin{itemize}

\item Aditya Chilukuri (Graduation: semester 1, 2022) Bachelor of Advanced Computing 
\item Hou (Harris) Loi (Graduation: semester 2, 2022) Bachelor of Advanced Computing 
\item Jack Kilrain (Graduation: semester 2, 2022) Bachelor of Software Engineering 
\item Junming Zhao (Graduation: semester 1, 2023) Bachelor of Engineering and Advanced Computing 
\item Anson Thai (Graduation: semester 1, 2024) Bachelor of Advanced Computing
\item Adnan Hasnat (Graduation: semester 2, 2025) Bachelor of Advanced Computing
\item Kshama Patel (Graduation: semester 2, 2025) Bachelor of Advanced Computing

\end{itemize}

\section*{B.S. and M.S. Project Students}

\begin{itemize}

%\item Arjun Sharma (2024, ANU, PhB Advanced Studies Course, 6 units)
%\item Nicholas Arvanitellis (2024, ANU, PhB Advanced Studies Course, 6 units)
\item Yuki Misumi (2024, ANU, COMP8755, 12 units)
\item Adnan Hasnat (2024, ANU, COMP3770, 12 units)
\item Itay Yarom (2024, ANU, COMP3770, 12 units)
\item Rosalita Rosenberg (2023, ANU, PhB Advanced Studies Course, 6 units)
\item Zack Noyes (2023, ANU, PhB Advanced Studies Course, 6 units)
\item Peter Oslington (2023, S2, ANU, PhB Advanced Studies Course, 6 units)
\item Peter Oslington (2023, S1, ANU, PhB Advanced Studies Course, 6 units)
\item Chethin Weerakkody (2023, ANU, COMP3770, 12 units)
\item Angus Atkinson (2022, ANU, COMP3740, 6 units)
\item Anson Thai (2022, ANU, COMP3770, 6 units)
\item Anson Thai (2021, ANU, COMP2560, 6 units)
\item Aditya Chilukuri (2021, ANU, COMP3770, 6 units)
%\item Peixiao Zhao, Master of Computing (2021, ANU, COMP8755, 12 units)
%\item Hengjia Zhang, Master of Computing (2020, ANU, COMP8755, 12 units) 
%\item Ruben Peter Vervaeke, Master of Science (2017, Free University Brussels, Thesis)

\end{itemize}

\section*{Summer Scholars (ANU)}

\begin{itemize}

\item Itay Yarom (summer 2023)
\item Junming Zhao (summer 2022)
\item Qianhui Wang (summer 2022)
\item Xuechao Wang (summer 2022)
\item Anson Thai (summer 2021)
\item Angus Atkinson (summer 2021)

\end{itemize}

\section*{Research Assistants (Casual)}
\begin{itemize}
\item Cassandra Chun-Crogan, BSc, 2021 (December 2021 - May 2022)
\item Kshama Patel, BAC (R\&D), 2021 (December 2022 - Feb 2023)
\end{itemize}

\ignore{
\section*{Examiner (ANU)}

\begin{itemize}

\item    In 2022, the process was centralized
\item 	 COMP8800 Zixian Cai u5937495 2020 (24 units) 
\item 	 COMP3770 Calum Snowdon u6044174 2020 (6 units)
\item 	 COMP4560 Benjamin Chamberlain Gray u6677379 2021 (12 units)
\item 	 COMP4550 Jack Hendrick de Kleuver u5740954 2021 (24 units) 
\item 	 COMP4560 Yiluo Wei u6227375 2021 (12 units)
\item 	 COMP4550 Kunal Sareen u6509424 2021 (24 units)
\item 	 COMP8755 Zicheng Liu u6924878 2021 (12 units)
\item 	 COMP4550 Alexander Horvat u6048805 2021 (24 units)
\item 	 COMP4550 Matthew Law u6699654 2021 (24 units)

\end{itemize}
}


\section*{Peer Reviewing and Program Committees}
\begin{itemize}
\item Program Committee, International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS), 2026
\item Program Committee, IEEE/ACM International Symposium on Microarchitecture (MICRO), 2025
\item Program Committee, Scalable Optimization for Efficient and Adaptive Foundation Models (SCOPE), 2025 (workshop collocated with ICLR)
\item Program \textit{Co-Chair}, Virtual Machines and Language Implementations (VMIL), 2025 (workshop collocated with SPLASH)
\item Program Committee, International Symposium on Memory Management (ISMM), 2025
\item Invited Reviewer (multiple papers, 2024-2025), ACM Transactions on Architecture and Code Optimization (TACO)
\item Program Committee, International Symposium on High-Performance Computer Architecture (HPCA), 2025
\item Program Committee, International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS), 2025
\item External Program Committee, IEEE/ACM International Symposium on Microarchitecture (MICRO), 2024
\item Program Committee, ACM SIGPLAN International Conference on Managed Programming Languages and Runtimes (MPLR), 2024
\item Program Committee, International Symposium on Computer Architecture (ISCA), 2024
\item Program Committee, International Symposium on Performance Analysis of Systems and Software (ISPASS), 2024
\item ACM Student Research Competition (SRC) Selection Committee, International Conference on Parallel Architectures and Compilation Techniques (PACT), 2023
\item Program Committee, IEEE/ACM International Symposium on Microarchitecture (MICRO), 2023
\item Program Committee, High Performance Computational Biology (HiCOMB), 2023 (workshop collocated with IPDPS)
\item Program Committee, Modern Language Runtimes, Ecosystems, and VMs (MoreVMs), 2023 (workshop collocated with <Programming>) 
\item Program Committee, International Symposium on Memory Management (ISMM), 2023
\item ACM Student Research Competition (SRC) Selection Committee, International Conference on Parallel Architectures and Compilation Techniques (PACT), 2022
\item External Expert Reviewer, ACM SIGPLAN International Conference on Object-Oriented Programming Systems, Languages, and Applications (OOPSLA), 2022
\item Program Committee, IEEE/ACM International Symposium on Microarchitecture (MICRO), 2022
\item Program Committee, International Symposium on High-Performance Computer Architecture (HPCA), 2023
\item Program Committee, International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS), 2023
\item Program Committee, International Symposium on Memory Management (ISMM), 2022
\item Program Committee, International Symposium on Performance Analysis of Systems and Software (ISPASS), 2022
\item External Review Committee, International Symposium on Computer Architecture (ISCA), 2022
\item External Review Committee, IEEE/ACM International Symposium on Microarchitecture (MICRO), 2021
\item Program Committee, International Symposium on Memory Management (ISMM), 2021
\item External Review Committee, International Symposium on Computer Architecture (ISCA), 2021
\item External Review Committee, International Symposium on High-Performance Computer Architecture (HPCA), 2021
\item External Review Committee, ACM SIGPLAN International Conference on Object-Oriented Programming Systems, Languages, and Applications (OOPSLA), 2020
\item Shadow Program Committee, European Conference on Computer Systems (EuroSys), 2020
\item External Review Committee, International Symposium on Computer Architecture (ISCA), 2020
\item External Review Committee, International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS), 2020
\item Program Committee, Virtual Machines and Language Implementations (VMIL), 2019 (workshop collocated with SPLASH)
\item Student Volunteer Co-Chair, ACM SIGPLAN Conference on Programming Language Design and Implementation (PLDI), 2019
\item Program Committee, International Symposium on Memory Management (ISMM), 2019
\item Program Committee, Programming Across the System Stack (PASS), 2019 (workshop collocated with <Programming>) 
\item Program Committee, Programming Across the System Stack (PASS), 2018 (workshop collocated with  <Programming>) 
\item Artifact Evaluation Committee, ACM SIGPLAN International Conference on Object-Oriented Programming Systems, Languages, and Applications (OOPSLA), 2017  
\item Artifact Evaluation Committee, ACM SIGPLAN International Conference on Object-Oriented Programming Systems, Languages, and Applications (OOPSLA), 2016  
\item Artifact Evaluation Committee, ACM SIGPLAN Conference on Programming Language Design and Implementation (PLDI), 2018
\item Reviewer, J. Parallel Distrib. Comput. 72 (2012) 
\end{itemize}

\section*{Teaching}
\begin{itemize}
%\item Teaching Assistant for Computer Architecture (code E034110) at Ghent University during Spring 2014, 2015, 2016, 2017
\item Convener, ANU, 2021, Computer Architecture and Simulation (ENGN2219)
\item Convener, ANU, 2021, Computer Microarchitecture (COMP3710) 
\item Convener, ANU, 2022, Computer Systems and Organisation (ENGN2219)
\item Convener, ANU, 2022, Computer Microarchitecture (COMP3710) 
\item Convener, ANU, 2022, Systems, Networks, and Concurrency (COMP2310) 
\item Convener, ANU, 2023, Computer Systems and Organisation (ENGN2219) 
\item Convener, ANU, 2023, Computer Organization and Program Execution (COMP2300) 
\item Convener, ANU, 2023, Systems, Networks, and Concurrency (COMP2310) 
\item Convener, ANU, 2024, Computer Systems and Organisation (ENGN2219) 
\item Convener, ANU, 2024, Computer Organization and Program Execution (COMP2300)
\item Convener, ANU, 2025, Computer Architecture (ENGN2219) 
\item Convener, ANU, 2025, Computer Architecture (COMP2300)
\item Convener, ANU, 2025, Parallel Computer Architecture (COMP4045) 
\end{itemize}

%\section*{References}
%
%\begin{multicols}{2}
%
%    \noindent Professor Lieven Eeckhout \\
%    Ghent University\\
%    Belgium \\
%    %\Telefon\ +00 1 234 5678\\
%    \Letter\ \href{mailto:Lieven.Eeckhout@UGent.be}{Lieven.Eeckhout\textrm{@}UGent.be}
%
%\vfill\columnbreak
%
%    \noindent Kathryn S. McKinley\\
%    Google\\
%    USA\\
%    \Letter\ \href{mailto:KSMcKinley@Google.com}{KSMcKinley\textrm{@}Google.com}
%
%\end{multicols}

\end{document}

